---
title: "Tibbles_R_Club_May_31st"
author: "Akiva Shalit-Kaneh"
date: "May 30, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

## Chapter 10 Tibbles

# 10.5 Exercises

1.How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

As seen below, when you print a dataframe the whole dataframe is printed. When you print a tibble only the first 10 or so rows will be printed and only the columns that fit in the console.

```{r}
print(mtcars)
A <- as_tibble(mtcars)
print(A)
```


2.Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

df_tb <- as_tibble(df)
df_tb$x
df_tb[, "xyz"]
df_tb[, c("abc", "xyz")]
```

When using a tibble $x does not recognize that you are asking for xyz and gives an error message. when using single square [] xyz is converted to a factorial and when using df_tb[, c("abc", "xyz")] abc is converted to a dbl and xyz to a factorial.

3.If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

```{r}
mtcars_tb <- as_tibble(mtcars)
var <- "mpg"
mtcars_tb[[var]]
```

4.Practice referring to non-syntactic names in the following data frame by:

   1.Extracting the variable called 1.

   2.Plotting a scatterplot of 1 vs 2.

   3.Creating a new column called 3 which is 2 divided by 1.

   4.Renaming the columns to one, two and three.
   
   
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```
 1.
 
 
 
```{r}
annoying[[1]]
```

2.

```{r}
ggplot(annoying, aes(`1`, `2`)) +
  geom_point()
```

3.

```{r}
annoying_plus <- mutate(annoying, `3` = `2` / `1`)
```


4.
```{r}
annoying_plus_names <- rename(annoying_plus, One = `1`, Two = `2`, Three = `3`)
```


5. What does tibble::enframe() do? When might you use it?

```{r}
tibble::enframe(1:10)
```

This makes a tibble and adds a serial number column.


6.What option controls how many additional column names are printed at the footer of a tibble?

options(tibble.print_max = n, tibble.print_min = m): if more than m rows, print only n rows.
Use options(dplyr.print_min = Inf) to always show all rows.
Use options(tibble.width = Inf)


