---
title: "R_club-May_10th"
author: "Akiva Shalit-Kaneh"
date: "May 4, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Transformation

Below is a fix for not being able to download nycflights13 from:
https://github.com/rstudio/webinars/issues/2


```{r}
install.packages("https://cran.r-project.org/src/contrib/nycflights13_0.2.2.tar.gz", repos=NULL, method="libcurl")
```

To use view() you need to call on tidyverse first.
```{r}
library(nycflights13)
library(tidyverse)
```

## 5.2.4 Exercises

1.1 Flights with an arrival delay of 2 or more hours:
```{r}
one_one <- filter(flights, arr_delay >= 120)
```

1.2 Flew to Houston:
```{r}
one_two <- filter(flights, dest == 'HOU' | dest == 'IAH')
```

1.3 Were operated by United, American, or Delta:

```{r}
one_three <- filter(flights, carrier == 'UA' | carrier == 'AA' | carrier == 'DL')
```
or 

```{r}
one_three <- filter(flights, carrier %in% c('UA', 'AA', 'DL'))
```

1.4 Departed in summer (July, August, and September):

```{r}
one_four <- filter(flights, month %in% c(7, 8, 9))
```

1.5 Arrived more than two hours late, but didn’t leave late: Note that early planes have negative minute values.

```{r}
one_five <- filter(flights, arr_delay >= 120 & dep_delay <= 0)
```

1.6 Were delayed by at least an hour, but made up over 30 minutes in flight:

```{r}
one_six <- filter(flights, dep_delay >= 60, dep_delay-arr_delay > 30)
```

1.7 Departed between midnight and 6am (inclusive):

```{r}
one_seven <- filter(flights, dep_time <=600 | dep_time == 2400)
```

2. between() is a shortcut for x >= left & x <= right, implemented efficiently in C++ for local values, and translated to the appropriate SQL for remote tables.

```{r}
two_seven <- filter(flights, !between(dep_time, 601, 2359))
```

3. 
```{r}
summary(flights)
```

8255 departure times are missing. Other missing data are dep_delay 8255, 8713 arr_time, 9430 arr_delay.

4.All the examples have a known solution regardless of the NAs value.
Any number to the power of 0 is 1, any " " | True will return a vlue of true. Any False & "" will give false. The rule is that if the value is known regardless of NA that will be the default.

## Exercise 5.3.1

1. How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).

```{r}
df <- tibble(x = c(5, 2, NA))
arrange(df, desc(is.na(x)))
```

Or

```{r}
arrange(df, -(is.na(x)))
```

I did not understand this, does it work because TRUE values are first?
In the second example TRUE gets the value of -1 and the others 0, is that the reason for the descending order?

2.Sort flights to find the most delayed flights. Find the flights that left earliest.

# _Most delayed_
```{r}
arrange(flights, desc(dep_delay))

```
# _Left the earliest_
```{r}
arrange(flights, dep_delay)
```

3.Sort flights to find the fastest flights.

```{r}
arrange(flights, air_time)
```

4.Which flights travelled the longest? Which travelled the shortest?

```{r}
arrange(flights, distance)
```

EWR to LGA 17 miles

```{r}
arrange(flights, desc(distance))
```

JFK to HNL 4983 miles


## Exercise 5.4.1

1.
```{r}
select(flights, dep_time,  dep_delay, arr_time, arr_delay)
```


```{r}
vars <- c("dep_time", "dep_delay", "arr_time", "arr_delay")
select(flights, one_of(vars))
```



2.What happens if you include the name of a variable multiple times in a select() call?

```{r}
select(flights, dep_time,  dep_time, dep_time, arr_delay)
```

Select treats variables written twice or more as if they were written once.

3. one_of() is used with select as well but you have to first define a vector and put it into the vars varialble to use the function.


```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))
```

4. Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?

```{r}
select(flights, contains("TIME"))
```

This was surprising, contains() was not case sensitive. By default several of the select helper functions are not case sensitive.

starts_with(match, ignore.case = TRUE, vars = current_vars())

ends_with(match, ignore.case = TRUE, vars = current_vars())

contains(match, ignore.case = TRUE, vars = current_vars())

matches(match, ignore.case = TRUE, vars = current_vars())
 
# This can be changes by setting _ignore.case = FALSE_

## 5.5.2 Exercises

1. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
New_flights <- flights
New_flights_min <- mutate(New_flights, dep_time_min = dep_time %/% 100 * 60 + dep_time %% 100, sched_dep_time_min = sched_dep_time %/% 100 * 60 + sched_dep_time %% 100)
New_flights_Min <- select(New_flights_min, -dep_time, -sched_dep_time)
```
How can I swap columns, or place new columns in place of existing ones (I know I can use select( wanted column, everything() ).

2.Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?

```{r}
flights_new <- mutate(flights, arr_dep = arr_time - dep_time)
select(flights_new, air_time, dep_time, arr_dep, everything())
```

The variables dep_time and arr_time are in both hours and minutes and are not a continuous value. To fix this they should be converted to minutes as was done in question 1.

3. Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?

```{r}
(Compare <- select(flights, dep_time, sched_dep_time, dep_delay))
```

dep_delay is the result of subtracting sched_dep_time from dep_time.

4. Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().

```{r}
filter(flights, min_rank(desc(dep_delay))<=10)
```

using desc() in min_rank gived the largest values the smalest ranking and so asking for those with ranking <=10 is what we are looking for.

5. What does 1:3 + 1:10 return? Why?
```{r}
1:3 + 1:10
```

This results in an error

> Warning message:
In 1:3 + 1:10 :
  longer object length is not a multiple of shorter object length
  
This makes two vectors of different sizes and so they cannot be added to each other.

6. What trigonometric functions does R provide?

>Trigonometric Functions

Description

These functions give the obvious trigonometric functions. They respectively compute the cosine, sine, tangent, arc-cosine, arc-sine, arc-tangent, and the two-argument arc-tangent.

cospi(x), sinpi(x), and tanpi(x), compute cos(pi*x), sin(pi*x), and tan(pi*x).
